### 2019-04-05 papers/journal/synth-dia.tex
Dia is complete

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below] {\color{blue} { \textbf{$R_{3}$}}} (ee);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}

>>>>

	  %pm <-> ee
	  \path (ee) edge[bend left=30] node [below, text width=2.0cm] {{$R_{3}$,{\color{blue} { \textbf{{$Q_{a2} $}}}}, {\color{blue} {{ $ Q_{a7}$}}}, {\color{blue} {{$R_{2}$}}}}} (pm);
	   \path (pm) edge[bend left=30, text width=2.3cm] node [above,rotate=-45] {{$R_{2}$}, {$Q_{a7}$} $Q_{bc7}$, $R_{7}$, $Q_{c7}$, $Q_{a2}$} node [below,anchor=center] {\color{blue} { \textbf{$R_{3}$}}} (ee);
%	  \path (pm) edge[bend left=30] node [above,rotate=-45,text width = 2.5cm] {{R2} {Qa7} Qbc7, R7, Qc7, Qa2, \color{blue} { \textbf{R3}}} (ee);	    
	 % \end{scope}
